Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-26 paper/ijcai/paper.tex
another pass on RQ3

\begin{figure}[h]
		\centering
		\includegraphics[width=0.415\textwidth]{figures/performance.pdf}
		\vspace{-0.4cm}
		\caption{Delta Cost of Diagnosis ($\Delta{}C$) per $k$}
		\label{fig:diagnosis}
\end{figure}

@@

Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ considering all the 
cases where the predicate $\Delta{}C>0$ holds, \ie{}, it additionally excludes from the dataset
the cases of faults where the techniques perform equally for at least one $k$. 
To sum, although we observed a relatively small number of cases where $\Delta{}C$
is negative (\numOutPerformed) and a high number of cases $\Delta{}C$
is zero (\numEquallyPerformed), we conclude that there is a
considerable amount of cases where the use of \combpar{k} would be
very beneficial.
% On the left-hand-side, we show distributions of
% $\Delta{}C$, for different values of $k$, considering all cases where
% the predicate $\Delta{}C\geq{}0$ holds, \ie{}, we excluded the
% \numOutPerformed\ cases where \sfl{}$^{k}$ outperformed \combpar{k}
% (see Figure~\ref{fig:diagnosis}).

@@

In the following, we present statistical analysis of the techniques.
Table~\ref{table:st} reports descriptive statistics about the
distributions of $C$ for the techniques under different values of $k$.
In bold, we present the results of the $227$ faults that do not
comprise the cases that are result of the limitations mentioned before
(test design and fault of omission). The number in parentheses are
relative to the dataset including all data faults; \Sof{improve}note that results
for this dataset are \emph{not} encouraging.

These results show that \ds{}
improves \sfl{} in a mean of $6$ ($3.3\%$ on average) statements on
the average ranking of all faulty statements, when considering
$k=10$.
However, if we only consider
the faults which can benefit from our approach, we can observe that
there is a considerable amount of cases where the approach is actually
successful. For $k=5$, our approach achieves a mean improvement of
$41.1$ ($9.57\%$ on average) statements on the ranking and an
impressive maximum ranking improvement of $3171$ ($96.7\%$ on average)
statements. Whereas for $k=10$, \combpar{k} achieves a mean
improvement of $19$ ($13.35\%$ on average) statements on the ranking
and a maximum ranking improvement of $209$ ($73.7\%$ on average)
statements. Such difference is justified by the fact that entire files
are discarded in \combpar{5}, whose statements are included in the
ranking of \combpar{10}. Consequently, the improvements obtained by
the technique will not be as high if slicing on these additional files
is unable to aggressively and safely discard statements. This also
shows that slicing files, in addition to slicing statements from those
files, is very beneficial for fault localization performance.

>>>>

\begin{figure}[h]
		\centering
		\includegraphics[width=0.45\textwidth]{figures/performance.pdf}
		\vspace{-0.4cm}
		\caption{Delta Cost of Diagnosis ($\Delta{}C$) per $k$}
		\label{fig:diagnosis}
\end{figure}

@@

Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ considering all the 
cases where the predicate $\Delta{}C>0$ holds, \ie{}, it focuses only
on the cases \combpar{k} outperformed the baseline technique.
To sum, although we observed a relatively small number of cases where $\Delta{}C$
is negative (\numOutPerformed) and a high number of cases where $\Delta{}C$
is zero (\numEquallyPerformed), there is a
considerable amount of cases where $\Delta{}C$ is positive and for
those cases \combpar{k} seems very beneficial.
% On the left-hand-side, we show distributions of
% $\Delta{}C$, for different values of $k$, considering all cases where
% the predicate $\Delta{}C\geq{}0$ holds, \ie{}, we excluded the
% \numOutPerformed\ cases where \sfl{}$^{k}$ outperformed \combpar{k}
% (see Figure~\ref{fig:diagnosis}).

@@

In the following, we present statistical analysis of the techniques.
Table~\ref{table:st} reports descriptive statistics about the
distributions of $C$ for the techniques under different values of $k$.
In bold, we present the results for the $227$ faults corresponding to
the cases where $\Delta(C)\geq{}0$. The number in parentheses are
relative to the dataset including all faults.

%% These results show that \ds{}
%% improves \sfl{} in a mean of $6$ ($3.3\%$ on average) statements on
%% the average ranking of all faulty statements, when considering
%% $k=10$.

We observe the following when considering the faults which can benefit
from \comb\ (numbers in bold). For $k=5$, \comb\ achieves a mean
improvement of $41.1$ ($9.57\%$ on average) statements on the ranking
and an impressive maximum ranking improvement of $3171$ ($96.7\%$ on
average) statements. For $k=10$, \combpar{k} achieves a mean
improvement of $19$ ($13.35\%$ on average) statements on the ranking
and a maximum ranking improvement of $209$ ($73.7\%$ on average)
statements. Such difference is justified by the fact that entire files
are discarded in \combpar{5}, whose statements are included in the
ranking of \combpar{10}. Consequently, the improvements obtained by
the technique will not be as high if slicing on these additional files
is unable to aggressively and safely discard statements. This also
shows that slicing files, in addition to slicing statements from those
files, is very beneficial for fault localization performance.
